---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/seasmith/ggloop.svg?branch=master)](https://travis-ci.org/seasmith/ggloop)

# ggloop

> Create ggplot2 plots in a loop.

## Overview
ggloop allows the user to use create multiple 'ggplot2' plots. Plots are created by passing multiple aesthetics via a vector of aesthetics to `ggloop()`. Users can use both dplyr-like syntax (i.e. `x = mpg:hp`, `y = 1`, `color = 4:8`, etc) and ggplot2-like syntax (i.e `x = mpg/cyl`, `y = wt + hp`, `color = factor(cyl)`, etc).

## Installation
```{r, eval=FALSE}
## CRAN
install.packages("ggloop")

## GitHub
devtools::install_github("seasmith/ggloop")  
```

## Where can I learn how to use ggloop?
You can see `ggloop` in action with the intro vignette (`vignette("intro", "ggloop")`). You can also see the example and  the very brief overview available below.

### A simple example

```{r example, warning=FALSE, message=FALSE}
library(ggloop)
library(ggplot2)
g <- ggloop(data = mtcars, 
            mappings = aes_loop(x = c(mpg:hp, mpg/cyl), 
                                y = c(hp:mpg, disp/hp),
                                color = gear), 
            remap_xy = FALSE)
g <- g %L+% geom_point()
g$color.gear$x.mpg_y.hp
```

### The functions

`ggloop` has three exported functions: 

* `ggloop(data, mappings = aes_loop(), remap_xy = TRUE, remap_dots = FALSE, ..., environment = parent.frame() )`
    * Mimicks `ggplot2::ggplot()` and its arguments.
    * Returned values:
	    * A single ggplot object = Created by `x`, `y`, and `...` arguments of length one or less.
	    * A list of ggplot objects = Created when there is no `...` argument in `aes_loop()`.
	    * A nest list (a list of a list) of ggplot objects = Created when a `...` argument is supplied. `...` names sit on the top-level of the nested list (they divide the list into however many parts based on the number of such arguments and the remapping behavior). `x` and `y` sit at the bottom-level of the nested list
* `aes_loop()`
    * Mimicks `aes()`
    * Accepts vectors of values for each argument.
    * Arguments with more than one value must be wrapped by `c()` and NOT have any nested `c()`.
  	* Syntax:
       	* `dplyr-like` = `mpg:hp`, `1`, `5:9`, `cyl`, etc.
	      * `ggplot2-like` = `factor(cyl)`, `gear + cyl`, etc.
	      * Both syntax styles can be combined for one argument using the `c()` as a wrapper and only `c()`.
* `%L+%`
    * Is a `+` operator for a nested list, list, or single 'ggplot' object.
