---
title: "Intro to ggloop"
author: "Luke Smith"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to ggloop}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Table of Contents

* [Overview](#overview)
* [Main Functions](#main-functions)
    * [ggloop](#ggloop)
    * [aes_loop](#aes_loop)
    * [+.gglist](#gglist)
* [Trivial Examples](#trivial-examples)
    * [Example 1](#example-1)
    * [Example 2](#example-2)
    * [Example 3](#example-3)

# Overview

`ggloop`'s main function is `ggloop()`, and it allows the user to create one of two things:

1. Multiple `ggplot2` plots.
2. A list of aesthetics, which can used to make `ggplot2` plots using `ggplot()`.

Instead of passing a single aesthetic (`x`, `y`, `...`) to `ggplot()`, the user can pass multiple aesthetics by using a vector of aesthetics. "Remapping"" behaviors control how the `x` and `y` vectors are paired with one another, and they control how mutliple `...` arguments are paired with
one another.

The `gg_obs` argument controls the returned value: either `ggplot2` plots or a list of aesthetics which can be used to make `ggplot2` plots. `gg_obs`'s default value is `TRUE`, which instructs `ggloop()` to return plots. `FALSE` instructs `ggloop()` to return a list of aesthetics.

---

# Main Functions

## `ggloop`

Mimicry of `ggplot()`'s arguments (for the most part).

##### Args  

* `data` = Same as `data`
* `mappings` = Same as `mapping`, except `aes_loop()` is used in place of `aes()`. There currently is no support for a "strings"-type function.
* `remap_xy` = Controls the "remapping" behavior of the `x` and `y` vectors. Default = `TRUE`; other options include `FALSE` and `NA`.
    + `TRUE` = acts like `expand.grid()` except that exact duplicates (i.e. `x <- mpg; y <- mpg`) and unordered-pair duplicates (i.e. `x <- mpg; y <- cyl` and `x <- cyl; y <- mpg`) are removed.
    + `FALSE` = acts like R's internal recycling mechanism, which replicates the shorter of the two vectors however many times necessary to pair with the longer vector.
    + `NA` = leaves an unpaired vector element unpaired (i.e. `x = (mpg, wt, hp); y = (cyl, gear)` produces `x <- hp` with no y mapping)
* `remap_dots` = Controls the "remapping" behavior of the `dots` arguments. Default = `FALSE`; other option is `FALSE`.
    + `TRUE` = acts like R's internal recycling mechanism, which replicates the shorter of the two vectors however many times necessary to pair with the longer vector.
    + `FALSE` = leaves un unpaired vecotr element unpaired; similar to `remap_xy = NA` behavior.
* `gg_obs` = Controls the returned value. `TRUE` (default) returns `ggplot2` plots; `FALSE` returns a list of aesthetics (see [Value](#value)).
* `...` = The same as `...`; directly passed to `ggplot()`.
* `environment` = The same as `environment`; directly passed into `ggplot()`.

##### Value

There are two main types of returned values when `gg_obs = TRUE`:

  1. A list of `ggplot2` plots - when no `...` are specified in `aes_loop()`.
  2. A nested list (a list of a list) of `ggplot2` plots - when there are `...` specified in `aes_loop()`.

## `aes_loop`

Mimicry of `ggplot()`'s `aes()`, except:

  1. You can use `dplyr`'s syntax to call variables (i.e. `y = mpg:cyl`, `x = 1:5`, etc). You can still use `ggplot2`'s syntax to call variables (i.e. `x = disp`, `x = mpg/hp`, `color = factor(cyl)`, `y = gear + cyl`, etc). You can also use both within a vector, but do adhere to the rule below.
  2. If you are calling more than one variable, then you need to wrap the variables in `c()` and not have any other `c()` within that wrapping (i.e. `x = c(mpg:cyl, 5, 6:8, gear + cyl, mpg/hp)`, `color = c(factor(cyl), factor(gear))`).

##### Args

* `x` = Same as `x`
* `y` = Same as `y`
* `...` = Same as `...`

## `+.gglist`

A `+` operator method for objects with class `gglist` (the returned objects of `ggloop()`). `+.gglist` will add features to plots in both:

  1. A list of `ggplot2` plots.
  2. A nested list (a list of a list) of `ggplot2` plots.
  
Users can `+.gglist` by calling `+`, like they would when using `+.gg` from the `ggplot2` package. Much like `+.gg`, the results of `+.gglist` will not be saved unless the result is assigned.


---

# Trivial Examples

## Example 1

**Example:** Using the `mtcars` data set, create and plot all possible xy-pairs between `mpg` and `hp`.  
**Steps:** Load the necessary packages, create plots with `ggloop()`, and add to plots using `+.gglist`.

```{r xy-pairs, message=FALSE}
library(ggplot2)
library(ggloop)
g <- ggloop(mtcars, aes_loop(x = mpg:hp, y = mpg:hp))

# View some plots
g$x.mpg_y.hp + geom_point()
g$x.cyl_y.disp + geom_point()
g$x.disp_y.hp + geom_point() + geom_line()


# Use `+.gglist` to add to two plots, save the output, and then display the results.
g[1:2] <- g[1:2] + geom_point()
g[1:2]
```

Look at the mappings of each name in `g`. Note how the list is NOT nested (because no `...` were called in `aes_loop()`).
```{r simple-3}
lapply(g, `[[`, "mapping")
```

## Example 2

**Example:** Plot `c(mpg, disp, hp)` against `wt` and facet the resulting plots.  
**Steps:** Create plots, add geoms, and add `facet_grid()`.  

```{r facet-1}
g2 <- ggloop(mtcars, aes_loop(x = c(mpg, disp, hp), y = wt, color = factor(cyl))) +
  geom_point() +
  facet_grid(. ~ cyl)

# View some plots
g2$`color.factor(cyl)`[1:3]

# Look at the mappings of each name in `g2`. Note how the list is nested
# (because a `...` argument was called in `aes_loop()`).
lapply(g2, function(x) lapply(x, `[[`, "mapping"))
```

## Example 3

**Example:** Return the list of aesthetics rather than the list of plots.  
**Steps:** Call `ggloop()` with `gg_obs = FALSE`.

```{r aes.list-1}
g3 <- ggloop(mtcars,
             aes_loop(x = c(mpg, disp, hp), y = wt, color = c(factor(cyl), factor(gear))), 
             gg_obs = FALSE)
print(g3)
```
