---
title: "Looping and Adding"
author: "Luke Smith"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

FRED series to scrape:
* All Employees: Total Nonfarm in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264200000000001A)	
* All Employees: Real Estate and Rental and Leasing in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264205553000001A)	
* All Employees: Professional, Scientific, and Technical Services in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264206054000001A)	
* All Employees: Utilities in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264204322000001A)	
* All Employees: Government in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264209000000001A)	
* All Employees: Retail Trade in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264204200000001A)	
* All Employees: Legal Services in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264206054110001A)
* All Employees: Construction in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264202000000001A)	
* All Employees: Mining: Oil and Gas Extraction in Houston-The Woodlands-Sugar Land, TX (MSA)
* All Employees: Manufacturing in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264203000000001A)	
* All Employees: Health Care and Social Assistance in Houston-The Woodlands-Sugar Land, TX (MSA) (SMU48264206562000001A)	

---
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
